The human in the loop: volunteer computing as a socio-technical system

### 2016-02-29 Alife16/paper.tex
Accepting changes by @mariosky
But don't erase graphs, although it's easy to generate them, we might need them in its current state later on.

The next Section will describe experiments performed to
establish a baseline performance and gather initial performance
results. In the experiments performed last year we used the 40-trap
problem, while the current experiments changed to the more difficult 50-trap
in order to compare the performance with a more computationally intensive problem.

>>>>

The next Section will describe experiments performed to
establish a baseline performance and gather initial performance
results. In the first set of experiments, performed last year, we used the 40-trap
problem, while the current experiments changed to the more difficult 50-trap
in order to compare the performance with a more computationally intensive problem.
